Autonomous Quadrotor Landing on a Moving Platform

### 2016-04-21 docs/report/report.tex
Update report

% DOCUMENT PADDING AND MARGINS
\usepackage{titlesec}
\usepackage[margin=0.8in]{geometry}
\setlength{\parskip}{\baselineskip}
%\setlength{\parindent}{0pt}
\titlespacing*{\section}{0pt}{2ex}{0ex}
\titlespacing*{\subsection}{0pt}{2ex}{0ex}
\titlespacing*{\subsubsection}{0pt}{2ex}{0ex}

@@

\subsection{Controller and State Monitoring}
In this project it is assumed that the quadrotor has successfully rendezvoused with the target vehicle and at all points in time has a clear view through the camera image of the landing target located on the target vehicle. The first step of performing  autonomous landing is to position the quadrotor above the landing target such that the displacements in the x and y directions in the horizontal plane normal to the landing surface are near zero while simultaneously matching speed with the target vehicle. Next, while maintaining the near zero displacements in the x and y directions, the quadrotor must begin to descend at a safe rate such that the vertical distance between the quadrotor and the landing target is reduced until landing is achieved. Ideally the quadrotor will descend more rapidly when the vertical displacement between the qaudrotor and target is large, slowing down just before it hits the target in order to minimize time and energy requirements of the landing Vancouver.

In order to achieve the described behaviour, a set of 3 of PID controllers are developed, one for the x, y and z directions respectively. During all stages of landing the x and y PID controllers work to minimize the displacement between the target and the qaudrotor which also has the side effect of maintaining the velocity relative to the target. During the approach the PIDz controller attempts to maintain a safe approach altitude such that the target does not go out of view during stage one. Once a these hold displacement value in x and y is achieve the $PID_z$ controller is set a set of commands that smoothly move the quadrotor to a landing position.

@@

\begin{equation}
\label{PIDx}
	\psi_t = cos(\theta) \left( K_p e_x + K_i \sum_{t=0}^{t} \dot{e_x}_{,t} dt + K_d \dot{e_x}_{,t}) \right)
\end{equation}

@@

>>>>

% DOCUMENT PADDING AND MARGINS
\usepackage{titlesec}
\usepackage[margin=0.8in]{geometry}
%\setlength{\parskip}{\baselineskip}
%\setlength{\parindent}{0pt}
\titlespacing*{\section}{0pt}{2ex}{0ex}
\titlespacing*{\subsection}{0pt}{2ex}{0ex}
\titlespacing*{\subsubsection}{0pt}{2ex}{0ex}

@@

\subsection{Controller and State Monitoring}
In this project we assumethat the quadrotor has successfully rendezvoused with the target vehicle and at all time has a clear view through the camera image of the landing target located on the target vehicle. The first step towards autonomous landing is to position the quadrotor above the landing target such that the displacements in the x and y directions in the horizontal plane normal to the landing surface are near zero while simultaneously matching speed and aligning the axis with the target vehicle. Next, while maintaining the near zero displacements in the x and y directions, the quadrotor must begin to descend at a safe rate such that the vertical distance between the quadrotor and the landing target is reduced until landing is achieved. Ideally the quadrotor will descend more rapidly when the vertical displacement between the qaudrotor and target is large, slowing down just before it hits the target in order to minimize time and energy requirements of the landing Vancouver.

In order to achieve the described behaviour, we developed a PID position controller that outputs attitude commands to reduce the horizontal and vertical distance between the quadrotor and the landing platform. During the approach the PIDz controller attempts to maintain a safe approach altitude such that the target does not go out of view during stage one. Once a these hold displacement value in x and y is achieve the $PID_z$ controller is set a set of commands that smoothly move the quadrotor to a landing position.

@@

\begin{equation}
	\label{PIDx}
	\hat{\psi_t} = cos(\theta) \left(K_p e_x + K_i \sum_{t = 0}^{t} e_{x, t} dt + K_d \dot{e}_{x,t} \right)
\end{equation}q

@@

\begin{figure*}
	\centering
	\includegraphics[width=\textwidth]{images/PID_x.eps}
	\caption{Position Controller - Roll Command}
	\label{fig:apriltagInception}
		\vspace{-0.4cm}
\end{figure*}

\begin{figure*}
	\centering
	\includegraphics[width=\textwidth]{images/PID_y.eps}
	\caption{Position Controller - Pitch Command}
	\label{fig:apriltagInception}
		\vspace{-0.4cm}
\end{figure*}

\begin{figure*}
	\centering
	\includegraphics[width=\textwidth]{images/PID_Elevation.eps}
	\caption{Position Controller - Throttle Command}
	\label{fig:apriltagInception}
\end{figure*}
